Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-19 papers/clusters.tex
Some zeroth text and notes on M13

The abundances we find for clusters identified in k-space are consistent
with detailed studies in the literature.

>>>>

The abundances we find for clusters identified in k-space are in excellent
agreement with detailed studies that exist in the literature. The mean
metallicity for stars we identify in abundance space that are later attributable
to M13 have a mean of [Fe/H]$ = -1.55$, in agreement with other works \citep{Kraft_1992,Cohen_Melendez,Johnson_Pilachowski} and the \citet{Harris} catalog.
The detailed abundances are also in agreement: we find a correlation in 
[C/Fe] and [N/Fe] abundances, and an intrinsic spreads in each element
that reflects deep mixing along the red giant branch.

% M13
% ANDY IS EDITING AND COLLECTING CRAP HERE.
We have a smaller spread in [O/Fe] than Johnson & Pilachowski (http://iopscience.iop.org/article/10.1088/2041-8205/754/2/L38/pdf)
Theirs is -1 to +1

The mean of [Na/Fe] and [O/Fe] is consistent with J & P.

%\bibitem[Johnson 
%\& Pilachowski(2012)]{2012ApJ...754L..38J} Johnson, C.~I., \& Pilachowski, C.~A.\ 2012, \apjl, 754, L38

Our [N/Fe] and [C/Fe] overlaps perfectly with Smith et al (2005). Our scatter in [C/Fe] is slightly less: this is because those with the lowest [C/Fe] ratios are the brightest cluster members, which are not in this cluster (e.g., lowest Teff is ~4500) -- did APGOEE observe them?

%\bibitem[Smith et al.(2005)]{2005AJ....129.1589S} Smith, G.~H., Briley, 
%M.~M., \& Harbeck, D.\ 2005, \aj, 129, 1589

C-depletion wrt Teff (due to mixing) also seen in

 \bibitem[Briley et al.(2004)]{2004AJ....127.1579B} Briley, M.~M., Cohen, 
J.~G., \& Stetson, P.~B.\ 2004, \aj, 127, 1579

% Abundances (Mg, Al, Na, O, Fe, and probably other projections) perfectly consistent with 
%\bibitem[Cohen 
%\& Mel{\'e}ndez(2005)]{2005AJ....129..303C} Cohen, J.~G., \& Mel{\'e}ndez, J.\ 2005, \aj, 129, 303

and

%\bibitem[Kraft et al.(1992)]{1992AJ....104..645K} Kraft, R.~P., Sneden, C., 
%Langer, G.~E., \& Prosser, C.~F.\ 1992, \aj, 104, 645 
% except perhaps we have fewer low [O/Fe] objects than Kraft et al.

% Palomar 5

% Sagittarius "star cloud"?
% Fig 6: high-velocity-dispersion structure in the Galactic halo.
